---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.retina = 2
)
```

# covidutils

<!-- badges: start -->
<!-- badges: end -->

Centralised utility functions for covid related projects at Epicentre.

## Installation

Install covidutils from github with:

``` r
remotes::install_github("epicentre-msf/covidutils")
```

## Development

To include a function in the package, add it to a script in the `R/` directory. 

### Best practices

- Large functions should have their own `.R` script inside the `R/` directory with an information name, `get_ecdc.R` for example
- Smaller utility functions can be grouped into a single script such as `utils.R`
- If you are using functions used from external packages inside your own function, they must be fully qualified i.e. `dplyr::filter()`
- All external packages used must be added to the imports section of the `DESCRIPTION` file. This can be done via `usethis::use_package("name_of_package")`
- All variables used within a function should be passed as arguments
- Document your functions using [roxygen syntax](https://roxygen2.r-lib.org/)
- When your changes are ready and documented:
  - run `devtools::document()` to build the appropriate documentation files
  - run `devtools::check()` to check the package for any errors or warnings
  - run `devtools::install()` to install or re-install the package on your system
  - consider adding a usage of example of any new functions in this `README.Rmd` below then knit the document to produce the `.md` format required for github
  - push the changes to github
  
If using RStudio, you can document, check and install the package with option in the 'Build' pane.

When developing new functions you can run `devtools::load_all()` at anytime load the current state of all function in the `R/` directory.

Further R package development resources:

- [Hadley Wickham's R Packages book](https://r-pkgs.org/) (free online)
- [Karl Broman's R package primer](https://kbroman.org/pkg_primer/)
- [Hilary Parker's R package from scratch tutorial](https://hilaryparker.com/2014/04/29/writing-an-r-package-from-scratch/)

## Function examples

```{r example}
library(tidyverse)
library(covidutils)
```

### Import JHU CSSE data

```{r}
df_covid <- get_owid_jhcsse()
glimpse(df_covid)
```

### Compute 14 and 30 day case and death trends

```{r}
df_trends <- get_country_summaries(df_covid)
glimpse(df_trends)
```

```{r}
# country with fastest growing case numbers in last 14 days
(iso <- df_trends %>% 
  filter(trend_cases_coeff_14d == max(trend_cases_coeff_14d, na.rm = TRUE)) %>% 
  pull(iso_a3))
df_country <- df_covid %>% filter(iso_a3 == iso)
df_trends_country <- df_trends %>% filter(iso_a3 == iso)

```

```{r}
country_plot(df_country, df_trends_country, add_title = TRUE)
```

```{r}
country_table(df_trends_country)
```

